Comparison among doublet predictions on benchmarking datasets

### 2024-06-17 analyses/doublet-detection/exploratory-notebooks/03_compare-benchmark-results.Rmd
add more PCAs, per review

```{r}
plot_pca_calls <- function(df, 
                           color_column, 
                           pred_column,
                           title) {
  # Plot PCs colored by singlet/doublet, showing doublets on top
  # df is expected to contain columns PC1, PC2, `color_column`, and `pred_column`. These should _not_ be provided as strings
  ggplot(df) + 
    aes(x = PC1, 
        y = PC2, 
        color = {{color_column}}) +
  geom_point(
    size = 0.75, 
    alpha = 0.6
  ) +
  scale_color_manual(name = "", values = c("black", "gray80")) + 
  geom_point(
    data = dplyr::filter(df, {{color_column}} == "doublet"), 
    color = "black",
    size = 0.75
  ) +
  ggtitle(title) +
  theme(
    legend.title.position = "top",
    legend.position = "bottom"
  )
}

plot_pca_metrics <- function(df, color_column, metric_colors) {
  # Plot PCs colored by performance metric, showing false calls on top
  # metric_colors is a named vector of colors used for coloring tp/tn/fp/fn
  # df is expected to contain columns PC1, PC2, and `color_column`. This should _not_ be provided as a string.
  ggplot(df) + 
    aes(x = PC1, 
        y = PC2, 
        color = {{color_column}}) +
  geom_point(
    size = 0.75, 
    alpha = 0.6
  ) + 
  geom_point(
    data = dplyr::filter(df, {{color_column}} %in% c("fp", "fn")), 
    size = 0.75
  ) +
  scale_color_manual(name = "Call type", values = metric_colors) +
  theme(legend.position = "bottom")
}
```

@@

MORE MORE MORE MORE MORE FILL IN THIS TEXT!!!

This section plots the PCA for each dataset, with three color schemes from left to right:

1. Ground truth doublets are shown in black and singlets in blue
2. Consensus doublets are shown in black and all remaining droplets in blue
3. Points are colored based on comparing the consensus call to the ground truth as one of:
  - true positive (`tp`), true negative (`tn`), false positive (`fp`), false negative (`fn`)

@@

      p3 <- plot_pca_calls(
        df, 
        color_column = cxds_prediction, 
        color_lab = "cxds prediction"
      )

@@

      # combine and plot
      plot( 
        (p1 + p2 + p3) / (p4 + p5 + p6) + 
          plot_annotation(glue::glue("PCA for {dataset}")) + 
          plot_layout(guides = "collect"))
    }
  )
```

>>>>

```{r}
plot_pca_calls <- function(df, 
                           color_column, 
                           pred_column,
                           title) {
  # Plot PCs colored by singlet/doublet, showing doublets on top
  # df is expected to contain columns PC1, PC2, `color_column`, and `pred_column`. These should _not_ be provided as strings
  ggplot(df) + 
    aes(x = PC1, 
        y = PC2, 
        color = {{color_column}}) +
  geom_point(
    size = 0.75, 
    alpha = 0.6
  ) +
  scale_color_manual(name = "", values = c("black", "gray80")) + 
  geom_point(
    data = dplyr::filter(df, {{color_column}} == "doublet"), 
    color = "black",
    size = 0.75
  ) +
  ggtitle(title) 
}

plot_pca_metrics <- function(df, color_column, metric_colors) {
  # Plot PCs colored by performance metric, showing false calls on top
  # metric_colors is a named vector of colors used for coloring tp/tn/fp/fn
  # df is expected to contain columns PC1, PC2, and `color_column`. This should _not_ be provided as a string.
  ggplot(df) + 
    aes(x = PC1, 
        y = PC2, 
        color = {{color_column}}) +
  geom_point(
    size = 0.75, 
    alpha = 0.6
  ) + 
  geom_point(
    data = dplyr::filter(df, {{color_column}} %in% c("fp", "fn")), 
    size = 0.75
  ) +
  scale_color_manual(name = "Call type", values = metric_colors) +
  ggtitle("Consensus call metrics")
}
```

@@

This section plots the PCA for each dataset, clockwise from the top left:

1. `scDblFinder` singlet/doublet calls. 
2. `scrublet` singlet/doublet calls
3. `cxds` singlet/doublet calls 
4. Ground truth single/doublets
5. Consensus singlet/doublet calls
6. Points are colored based on comparing the consensus call to the ground truth as one of:
    - true positive (`tp`), true negative (`tn`), false positive (`fp`), false negative (`fn`)

For the first five panels, doublets are shown in black and singlets in light gray.

@@

      p3 <- plot_pca_calls(
        df, 
        color_column = cxds_prediction, 
        title = "cxds prediction"
      )

@@

      # combine and plot
      plot( 
        (p1 + p2 + p3) / (p4 + p5 + p6) + 
          plot_annotation(
            glue::glue("PCA for {dataset}"), 
            theme = theme(plot.title = element_text(size = 16))) + 
          plot_layout(guides = "collect"))
    }
  )
```
